---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
opts_chunk$set(echo=TRUE, fig.path='figure/')
```


Load some useful packages:
```{r load_packages, message=FALSE}
library(dplyr)
```


## Loading and preprocessing the data
```{r load_data}
dataFile <- 'activity.csv'
activity <- read.csv(dataFile, 
                     colClasses=c("numeric", "POSIXct", "numeric"))
activity <- tbl_df(activity)
```

## What is mean total number of steps taken per day?
```{r total_steps}
activity_by_day <- activity %>% group_by(date)
by_day <- summarize(activity_by_day, total_steps=sum(steps))
```
```{r echo=FALSE}
# summarize(activity_by_day, mean(steps))
# activity_by_day <- mutate(activity_by_day,
#                           total_steps=sum(steps),
#                           mean_steps = mean(steps),
#                           median_steps = median(steps))
```

The experiment was conducted for `r tally(by_day)` days
(from `r min(by_day$date)` to `r max(by_day$date)`).

1. The total number of steps taken per day is
```{r}
by_day$total_steps
```

2. The histogram of the total number of steps taken each day is as follows:
```{r histogram_total_steps, fig.height=4}
hist(by_day$total_steps, breaks=10,
     main="Total number of steps taken each day", xlab="Total steps")
```

3. The mean of the total number of steps taken per day is
```{r mean_total_steps}
mean_total_steps <- mean(by_day$total_steps, na.rm=TRUE)
mean_total_steps
```

The median of the total number of steps taken per day is
```{r median_total_steps}
median_total_steps <- median(by_day$total_steps, na.rm=TRUE)
median_total_steps
```

[//]: # (**zero** for all `r sum(!is.na(by_day$total_steps))` days without
missing values. Indeed, there are `r sum(by_day$median_steps != 0, na.rm=TRUE)`
days where the median is not zero.)

## What is the average daily activity pattern?


## Imputing missing values


## Are there differences in activity patterns between weekdays and weekends?
